Every Author as First Author

### 2023-03-30 paper.tex
Improve formatting of \textopacity

% Theme based on https://tex.stackexchange.com/a/283543/245104
\usepackage{xcolor}
\definecolor{commentgreen}{RGB}{2,112,10}
%\definecolor{eminence}{RGB}{108,48,130}
%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
\definecolor{ouridentifier}{RGB}{0,71,171} % cobolt blue
\definecolor{frenchplum}{RGB}{129,20,83}
\definecolor{stringorange}{RGB}{139,64,0} % dark orange
\definecolor{identifieryellow}{RGB}{82,81,0}
\usepackage{listings}
\lstset{
  language=[LaTeX]TeX,
  basicstyle=\ttfamily,
  numbers=left, numberstyle=\footnotesize,
  commentstyle=\slshape\color{commentgreen},
  alsoletter={@},
  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
  keywordstyle=\color{frenchplum},
  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
  emphstyle=\color{ouridentifier},
  stringstyle=\color{stringorange},
  identifierstyle=\color{identifieryellow},
  showstringspaces=false
  %texcsstyle=*\color{frenchplum}
}
\usepackage{multicol} % enables multicols=2

>>>>

% Theme based on https://tex.stackexchange.com/a/283543/245104
\usepackage{xcolor}
\definecolor{commentgreen}{RGB}{2,112,10}
%\definecolor{eminence}{RGB}{108,48,130}
%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
\definecolor{ouridentifier}{RGB}{0,71,171} % cobolt blue
\definecolor{frenchplum}{RGB}{129,20,83}
\definecolor{stringorange}{RGB}{139,64,0} % dark orange
\definecolor{identifieryellow}{RGB}{82,81,0}
\usepackage{listings}
\lstset{
  language=[LaTeX]TeX,
  basicstyle=\ttfamily,
  numbers=left, numberstyle=\footnotesize,
  commentstyle=\slshape\color{commentgreen},
  alsoletter={@},
  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open,pgfsetfillopacity,pgfpathmoveto,pgfpointorigin,pgftext},
  %morekeywords={pgfpicture},
  keywordstyle=\color{frenchplum},
  emph={textopacity,textstack,textstack@step,textstack@append,textstack@expand,namestack},
  emphstyle=\color{ouridentifier},
  stringstyle=\color{stringorange},
  identifierstyle=\color{identifieryellow},
  showstringspaces=false
  %texcsstyle=*\color{frenchplum}
}
\usepackage{multicol} % enables multicols=2
